Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-20 Answers_for_reviewers.tex

\title{Answers for the Reviewers  for the paper "Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes"}

\author{Emmanuel Franck\footnotemark[1] \footnotemark[2],
C. Buet \footnotemark[3], 
B. Despr\'es\footnotemark[4], 
T. Leroy\footnotemark[4] \footnotemark[3]
}
 \footnotetext[1]{INRIA Nancy Grand-Est and IRMA Strasbourg}
 \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
 \footnotetext[4]{Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
\footnotetext[2]{Email adress: emmanuel.franck@inria.fr}

\maketitle

\section{Answers for the report 2M}
\begin{itemize}
\item A massive overuse of ?Constant C? and the issue of the estimates? time-dependence
\begin{itemize}
\item Page 5 we have modified the constant for the 1D regularity mesh
\item We have correct the constant in the proposition 2.5 page 8
\item 1 : we have corrected the constant in the proposition 2.2 page 7
\item 8: in 1D we have explicit all the constant 
\item 3 :
\item 4 :
\item 5 : We have explicit the constant between the equation (32) and the end of the proof of the proposition 2.5
\item 6 :
\item 7 : The conflict for the notation have been corrected. For the solution there are not reference, we have construct this solution using a separation of the variable. we have added the details.
\item 2-8: in 1D we have explicit all the constant. We obtain time-exponential rate as you expect.
\end{itemize}
\begin{itemize}
\item Comments and suggestions
\begin{itemize}
\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
\item 2: we have added 2 sentences about the 2D Riemann problem and the nodal scheme. 
\item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme. For the remark about " the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character" it is not clear that we say that. Indeed the scheme is well balanced for a subset of steady states (see annex of the paper "design of AP scheme ..."): the steady state associated to $u=Cts$ and $p$ linear. This property is perhaps impotent for the uniform convergence. At the end we renounce only to the steady states associated to $\nabla{u}=\nabla\times \phi$ with $\phi$ a potential. 
\item 4: We have correct this part introducing $v$ to obtain a not confusing proof.
\item 5: We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
\item 6 : We have replaced the proposition 2.8 by the Lemma 2.8
\item 7 : We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
\item 8 : We have corrected the proposition 
\item 9 : We have added the missing "("
\end{itemize}
\item Minor issues and Typos
\begin{itemize}
\item 1: We have replaced $P^0$ by "first order"
\item 2 : we have corrected this sentence 
\item 3 : we have corrected this sentence 
\item 4 : we have corrected this sentence. (17) correspond to the scheme not the smooth data.
\item 5 : we have corrected this sentence. 
\item 6 : we have corrected your two remarks in this page 
\item 7 : we have corrected this sentence. 
\item 8: We have replaced $\gamma$ by $\tau$ in the numeric part.
\item 9: The date for the L. Gosse paper have been modified. for the S. Jin article we have copy the reference written on the website of S. Jin 
\end{itemize}
\end{itemize}
\end{document}

### 2015-03-20 Corrected_version.tex
corrections

To illustrate the theory and have a more quantitative version of the error estimates
studied in this work, we consider the academic square $\Omega=[0,1]^2$ and discretize the hyperbolic heat equation
of a mesh made with random quads. 
A random quad mesh is made of quads where the vertices are moved
randomly around their initial position, by a factor between 10\% and 30\%.
We use the fully implicit time discretization version of the 2D scheme
detailed in this work. The solution of the linear systems is computed via
an iterative GMRES algorithm, which converges smoothly in our numerical experiments.
The reference analytical solution used in our tests is designed by separation of variables.
A solution of (\ref{eq:mod1}) is
$$
p= f+\frac{\eps^2}\sigma \partial_t f
\mbox{ and }
\mathbf u= -\frac\eps \sigma \nabla f,
$$
with $f$ solution of 
$
\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0$.
We add periodic boundary conditions and consider
$$
f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y ).
$$
The function $\alpha$ is determined as the solution of
$$
\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2\pi}\sigma \alpha=0
$$
whith $\alpha'(0)=0$ and $\alpha(0)=1$.
For small $\eps$, which is the case we are interested in, the solution is computed as follows.
First determine 
$$
\lambda_1=-
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } +1\right)
}{2 \eps^2  }
\mbox{ and }
\lambda_2=
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } -1\right)
}{2 \eps^2  }.
$$
Then 
$$
\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
-
\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
$$
from which $p(t)$ and $\mathbf u(t)$ are easily recovered.

>>>>

To illustrate the theory and have a more quantitative version of the error estimates
studied in this work, we consider the academic square $\Omega=[0,1]^2$ and discretize the hyperbolic heat equation
of a mesh made with random quads. 
A random quad mesh is made of quads where the vertices are moved
randomly around their initial position, by a factor between 10\% and 30\%.
We use the fully implicit time discretization version of the 2D scheme
detailed in this work. The solution of the linear systems is computed via
an iterative GMRES algorithm, which converges smoothly in our numerical experiments.
The reference analytical solution used in our tests is designed by separation of variables.
A solution of (\ref{eq:mod1}) is
$$
p= f+\frac{\eps^2}\sigma \partial_t f
\mbox{ and }
\mathbf u= -\frac\eps \sigma \nabla f,
$$
with $f$ solution of 
\begin{equation}\label{telegraph}
\partial_t f +\frac{\eps^2}\sigma \partial_t^2 f -\frac1\sigma \Delta f=0.
\end{equation}
 We propose to construct a solution for a subset of small $\eps$ to validate the uniform convergence. Firstly we consider that the solution is a periodic solution on the square $\left[0,2\right]\times\left[0,2\right]$. For this we use the separation of the variables. We consider the following function
$$
f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y ).
$$
and we propose to find the function $\alpha(t)$ such that $f(t,x,y)=\alpha(t)\cos (\pi x ))\cos( \pi y )$ is a periodic solution of (\ref{telegraph}).
The function $\alpha$ is determined as the solution of
$$
\alpha'(t)+ \frac{\eps^2}\sigma\alpha''(t)+\frac{2\pi}\sigma \alpha=0
$$
with $\alpha'(0)=0$ and $\alpha(0)=1$.
For small $\eps$, which is the case we are interested in, the solution is computed as follows.
First determine 
$$
\lambda_1=-
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } +1\right)
}{2 \eps^2  }
\mbox{ and }
\lambda_2=
\frac{
\sigma \left( \sqrt{1-\frac{\eps^2}{\sigma^2}  8 \pi^2  } -1\right)
}{2 \eps^2  }.
$$
Then 
$$
\alpha(t)=\frac{\lambda_2}{\lambda_2-\lambda_1}e^{\lambda_1 t  }
-
\frac{\lambda_1}{\lambda_2-\lambda_1}e^{\lambda_2 t  }
$$
from which $p(t)$ and $\mathbf u(t)$ are easily recovered.
